---
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document: 
    keep_md: yes
---

# Using the `climproxyrecords` data package

After loading the package with `r library(climproxyrecords)`, all included data has been "lazy loaded". Date are not in memory yet, but are available when the name of an object is passed to the R interpreter.

```{r}
library(climproxyrecords)
library(dplyr)

marcott.proxies
```

## Subsetting

For each proxy compilation, all records are stored in a single dataframe. To access subsets of proxies use either base R's subsetting 

```{r}
subset(marcott.proxies, Proxy.type == "Uk'37")
```

or ``dplyr::filter`

```{r}
marcott.proxies %>% 
  filter(Proxy.type == "Uk'37")
```

## Split to a list

or make a list of dataframes, each a separate proxy record

```{r}
lst <- plyr::dlply(marcott.proxies, "ID")

lapply(lst[1:2], head)
```



## **Warnings**

Proxy.name does not identify a unique proxy record (for the Marcott data at least) because some cores have multiple proxies measured on them. This can perhaps be fixed.

```{r}
name.type <- marcott.proxies %>% 
  select(Proxy.name, Proxy.type) %>% 
  distinct()

name.type %>% 
  group_by(Proxy.name) %>% 
  mutate(n = n_distinct(Proxy.type)) %>% 
  filter(n > 1)
```


At present, things like the names of proxy types have been taken "as is" from the supplementary data to the publications. There may be multiple spellings of the same type.


## Get metadata

To get additional metadata for the proxies, look at corresponding `metadata` dataframe and reference/join by `ID`

```{r}
dplyr::left_join(marcott.proxies, marcott.metadata)

marcott.metadata %>% 
  filter(Proxy.name == "GeoB5844-2")
```




