---
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document: 
    keep_md: yes
---

# `climproxyrecords`

The `climproxyrecords` package supplies published proxy climate record data and
compilations. So far it includes data from:

* the Marcott et al (2013) and Shakun et al (2012) compilation

* the GISP2 Ice Core Temperature and Accumulation Data from Alley (2000)

* Uk'37 based proxy for core MD99-2275 from Sicre et al (2011)

* Alkenone based reconstruction for core ODP846 from Herbert et al (2010)

* Alkenone based reconstruction for core U1313 from Naafs et al (2012)

For the two compilations the package contains three dataframes: `proxies`,
`dating`, and `metadata` (e.g. `marcott.proxies`). These
contain the proxy data, associated carbon dating information, and metadata
respectively.

For the individual proxies there are similar dataframes.

`alley.accumulation`  

`alley.temperature`  


`sicre.2011.MD99_2275.age.model` 
 
`sicre.2011.MD99_2275.metadata` 
 
`sicre.2011.MD99_2275.temperature`  


`naafs.U1313.temperature`  

`naafs.U1313.metadata`  

`herbert.ODP846.temperature`  

`herbert.ODP846.metadata`

## Installation

`climproxyrecords` can be installed from Bitbucket like this: 

```{r, eval=FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}

devtools::install_bitbucket("ecus/climproxyrecords")
```

## Citing the data

For the compilations, please cite both the compilaton papers (Marcott et al 2013, Shakun et al
2012), and the original sources from which the data were extracted. A full
list of sources can be found in the metadata dataframes, e.g. `marcott.metadata`.


For the other records please cite the original papers. See the help files e.g.
`help(sicre.2011.MD99_2275.temperature)` for the correct citations.


# Using the `climproxyrecords` data package

After loading the package with `library(climproxyrecords)`, all included data has been "lazy loaded". Data are not in memory yet, but are available when the name of an object is passed to the R interpreter.

```{r, message=FALSE}
library(climproxyrecords)
library(dplyr)

marcott.proxies
```

## Subsetting

For each proxy compilation, all records are stored in a single dataframe. To access subsets of proxies use either base R's subsetting 

```{r}
subset(marcott.proxies, Proxy.type == "Uk'37")
```

or `dplyr::filter`

```{r}
marcott.proxies %>% 
  filter(Proxy.type == "Uk'37")
```

## Split to a list

or make a list of dataframes, each a separate proxy record

```{r}
lst <- plyr::dlply(marcott.proxies, "ID")

lapply(lst[1:2], head)
```



## **Warnings**

Core.location does not identify a unique proxy record (for the Marcott data at least) because some cores have multiple proxies measured on them. 

```{r}
name.type <- marcott.proxies %>% 
  select(Core.location, Proxy.type) %>% 
  distinct()

name.type %>% 
  group_by(Core.location) %>% 
  mutate(n = n_distinct(Proxy.type)) %>% 
  filter(n > 1)
```


At present, things like the names of proxy types have been taken "as is" from the supplementary data to the publications. There may be multiple spellings of the same type.


## Get metadata

To get additional metadata for the proxies, look at corresponding `metadata` dataframe and reference/join by `ID`

```{r}
dplyr::left_join(marcott.proxies, marcott.metadata)

marcott.metadata %>% 
  filter(Core.location == "GeoB5844-2")
```




